Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Fixed the commands
Made the figures 2x2
Added part of the motivation
Issue #15

\newcommand{\croder}{\textbf{Croder }}
\newcommand{\IDE}{\textbf{IDE }}
\newcommand{\eclipse}{\textbf{Eclipse }}

@@

\section{Introduction}
\section{Why integrate reviews into the IDE}
\section{Related work}

@@

\begin{figure}[hbt]
\begin{center}
	\includegraphics[width=0.8\columnwidth]{newinterface1.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface2.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface3.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface4.jpg}
\end{center}
\caption{Interface example}
\label{fig:newinterface}
\end{figure}

>>>>

\newcommand{\croder}{\textsc{Croder }}
\newcommand{\IDE}{\emph{IDE }}
\newcommand{\eclipse}{\emph{Eclipse }}

@@

\section{Introduction}
\section{Why integrate reviews into the IDE}

Interruptions are bad because they break the flow of work and cause more stress \cite{Spolsky,Mark2008}. 
Also, the interruptions that a developers faces are varied \cite{Czerwinski2004}, so trying to reduce that number
will bring benefit to the workflow. By integrating the code review submission process into the \ide we can 
reduce the time of the interruption. Also, because the developer never leaves the context of his work, we hope 
that the effects of this interruption will be minimal.

Integrating into the \ide has other benefits too. The \ide is the environment where the code lives. By taping into
this resource we can get a lot more information about what the developer what to review. For example, suppose
he wants to select a method for review. If that method is tightly couple with another one, than we can suggest that
he include that method as well. Also, the developer never leaves the context. He can very easily go back to code
to decide whether some snippet of code would be relevant or not to the reviewer.

Another advantage is that we can submit discrete notification when a review has been received. This, again,
reduces the distraction and makes it a lot easier to see what the review is about. By presenting the result of 
the review in the \ide the developer can see it in context. This makes it a lot easier to come back in the context
of the review and make sense of the comments.

\section{Related work}

@@

\begin{figure*}[hbt]
\begin{center}
	\includegraphics[width=0.8\columnwidth]{newinterface1.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface2.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface3.jpg}
	\includegraphics[width=0.8\columnwidth]{newinterface4.jpg}
\end{center}
\caption{Interface example}
\label{fig:newinterface}
\end{figure*}
